Think deep for reef resilience

### 2025-09-20 paper/paper_draft.qmd
Add acknowledgements and contributions sections to paper
Also add required citations for Makie and Julia (as per websites).

@@

@@

@@

@@

>>>>

All data preparation, modelling and analyses were performed using the Julia programming
language (The Julia Project; https://julialang.org/; [@bezanson2017]), with visualisations
created using the Makie ecosystem [@danisch2021].

@@

# Author Contributions

**Benjamin Grier:** conceptualisation, data curation, formal analysis, investigation,
methodology, visualization, writing – original draft, writing – review and editing. **Takuya
Iwanaga:** conceptualisation, data curation, formal analysis, investigation, methodology,
visualization, writing – original draft, writing – review and editing.
**\[BG: To be completed.\]**

@@

We acknowledge the contributions of Barbara Robson and Jessica Benthuysen to manuscript
preparation. This research was funded by the Reef Restoration and Adaptation Program, and
facilitated by the Australian Institute of Marine Science. We acknowledge thermal projection
data sourced from HighResCoralStress datasets, model parameterisation data sourced from the
Ecological Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition
probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
available from the Great Barrier Reef Marine Park Authority.

@@

The authors declare no conflicts of interest.

@@

The full reproducible investigation, and links to required data sources, can be found at
Grier and Iwanaga [-@grier2025].
